### 2018-04-16 includes/stringfuzz.tex
Removing some redundant text to make space for shifted Contributions title.

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}
We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project
contains \linesInFuzzer{} lines of code, it takes an average of
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be
installed from source, or from the Python PIP package repository.

>>>>

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}
We organized \fuzzer{} to be easily extended. To show this, we note that while
the whole project contains \linesInFuzzer{} lines of code, it takes an
average of \linesPerX{} lines of code to create a transformer. \fuzzer{} can
be installed from source, or from the Python PIP package repository.

### 2018-04-16 includes/suites.tex
Removing some redundant text to make space for shifted Contributions title.

In this section, we describe the benchmark suites we generated
with \fuzzer{}, and on which we conducted our experimental
evaluation. Table~\ref{tbl:generated} describes the string
and regex instances that were
generated by \generator{}. Table~\ref{tbl:transformed} lists benchmarks
derived from existing seed instances by iteratively applying \transformer{}.
Every transformed instance is named according to its
seed and the transformations it undertook. For example,
\texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
\textit{Fuzz} and then \textit{Graft} to \texttt{z3-regex-1.smt2}.

The \textit{Amazon} category contains 472 instances derived from two seeds
supplied by our industrial collaborators. The \textit{Regex} category is
seeded by the \usOld{} regular expression test suite~\cite{z3str2-tests}. This
test suite contains 42 instances dealing with a wide variety of regular
expressions. Through cumulative transformations we expanded the 42 seeds to 7,551 unique
instances. Finally, the \textit{Sanitizer} category is obtained from
five industrial e-mail address and IPv4 sanitizers.

>>>>

In this section, we describe the benchmark suites we generated
with \fuzzer{}, and on which we conducted our experimental
evaluation. Table~\ref{tbl:generated} lists instances that were
generated by \generator{}. Table~\ref{tbl:transformed} lists instances
derived from existing seed instances by iteratively applying \transformer{}.
Every transformed instance is named according to its
seed and the transformations it undertook. For example,
\texttt{z3-regex-1-fuzz-graft.smt2} was transformed by applying
\textit{Fuzz} and then \textit{Graft} to \texttt{z3-regex-1.smt2}.

The \textit{Amazon} category contains 472 instances derived from two seeds
supplied by our industrial collaborators. The \textit{Regex} category is
seeded by the \usOld{} regex test suite~\cite{z3str2-tests}, which contains
42 instances. Through cumulative transformations we expanded the
42 seeds to 7,551 unique instances. Finally, the \textit{Sanitizer} category
is obtained from five industrial e-mail address and IPv4 sanitizers.
